Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Wording

We now describe the constraint models and processes used in each stage. In the
text below we assume there are $n$ skipper and $b$ boats, with $m = b/2$
matches in a flight. In total there are $t = n(n-1)/2$ matches and $f = \lceil
n(n-1)/m  \rceil$ flights. We may use the schedule in Table \ref{tab1}, for 7
skippers and 6 boats, to help illustrate the constraint models. Our
descriptions of the models omit some minor details, however the models are
available to download here (give us a link or something).

>>>>

We now describe the constraint models and processes used in each stage. In the
text below we assume there are $n$ skippers and $b$ boats, with $m = b/2$
matches in a flight. In total there are $t = n(n-1)/2$ matches and $f = \lceil
n(n-1)/m  \rceil$ flights. We use the schedule in Table~\ref{tab1}, for 7
skippers and 6 boats, to help illustrate the constraint models. Our
descriptions of the models omit some minor details, however the models are
available to download\footnote{?? give us a link to the models}.
